A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-03-07 paper/paper1/ms.tex
Move text around
Ohmic Dissipation as the cause of lack of inflated sub Saturns

\subsection{Critical examination of the Parker Wind model}

@@

>>>>

@@

\subsection{The Ohmic Dissipation Cliff: Evaporative annihilation as the cause of a lack of sub-Saturns}
The Ohmic dissipation mechanism predicts a rapid inflation timescale leading to the complete evaporation of hot Saturns.  The Ohmic dissipation mechanism made two key observable predictions.  The Ohmic dissipation heating should become less efficient as irradiation increased past an equilibrium temperature of about 2000 K.  Second, hot Saturns should should runaway evaporation, whereas hot Jupiters should reach equilibrium---albeit inflated---radii after Gyr timescales.  Both of these outcomes predated data that could adequately validate them, and these outcomes differ from the behavior of other heating mechanisms, such as photoevaporation or tides.

\citet{2018AJ....155..214T} statistically favored Ohmic dissipation based on evidence for a turnover in the heating efficiency of hot Jupiters in a sample of 281 Giant planets.  Futhermore, \citet{2018AJ....155..214T} also highlighted the lack of inflated sub-Saturns as an anomaly: the observational capability exist to detect such sources in large numbers and yet they were not found.

This dearth of hot-Saturns has persisted into the \emph{TESS} era.  Figure XX highlights the region of highly irradiated close-in planets with $N=$\censor{x} planets accessed through the NASA Exoplanet Archive \censor{cite NExScI}.  \hatpb occupies a relative void in this region.

The observation that \hatpb---the only hot Saturn searched for atmospheric escape to date---exhibits mass loss indicative of a terminal fate leads us to a natural explanation for the dearth of inflated hot Saturns.  The inflationary lifetime of this class is so short that observing planets of this class is unlikely.  \hatpb appears to be one of the rare planets that we happen to catch a glimpse of before it has been completely annihilated.

We therefore attribute this cliff in the $m_p$ vs $R_p$ diagram to Ohmic dissipation.  \citet{2018AJ....155..214T} emphasized the positive feedback loop as a cause for the lack of sub-Saturns, and noted an alternative interpretation-- mass-dependent migration segregation.  While both scenarios are conceivable, the evidence of strong evaporation of \hatpb favors the evaporation scenario.  Futhermore, the runaway evaporation of hot-Saturns was naturally predicted by the Ohmic dissipation mechanism, whereas mass-dependent migration has only been developed as a post-diction.

We predict that the few other inflated hot-Saturn \hatpb-analogs should also show evidence for atmospheric escape.  These sources make excellent targets for \ion{He}{1} 10830 observations, and other atmospheric escape diagnostics.  The key figure-of-merit can be distilled to $\tau_\mathrm{infl}$, and ignoring the $\epsilon$ term.  Following \censor{Kempton} et al we define a Helium Spectroscopy Metric (HSM) defined as...
